\vskip-0.6in \Large Political Uncertainty

### 2015-03-23 GS-extension.tex
change to subtracting bribes from vote buyer B

\vskip.3in
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
						\[
						  v(z) = \alpha -\beta \cdot z
						\]
						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$. This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z'' 
							\begin{itemize}
								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
								\item Uncertainty comes from: log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for
							\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

@@

				  v(z) = \alpha -\beta \cdot z + a(z) + b(z) > 0

@@

@@

							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) + b(j) \leq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) + b(j) \leq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) + b(j)}{\beta} \leq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \leq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj

@@

									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \left(1- \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)\right) - b(j) \right] dj \\

@@

								  - W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1

>>>>

\vskip.3in
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
						\[
						  v(z) = \alpha -\beta \cdot z
						\]
						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$. This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z'' 
							\begin{itemize}
								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
								\item Uncertainty comes from: \textbf{log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for}
							\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

@@

				  v(z) = \alpha -\beta \cdot z + a(z) - b(z) > 0

@@

						\item Notice that a bribe from $B$ is subtracted because it makes the alternative \textit{less} attractive

@@

							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) - b(j) \leq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) - b(j) \leq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) - b(j)}{\beta} \leq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj

@@

									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \leq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj

@@

									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \left(1- \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)\right) - b(j) \right] dj \\

@@

								  - W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1
